---
title       : Group score presentation
subtitle    : 
author      : Lynette Garcia
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r echo=FALSE, results='hide'}
    library(ggplot2)
    #Loading data
    rendimiento<-read.csv("Notas - 100-rendimiento_1.csv",sep = ";")
    actFeatures<-read.csv("data/ponderacion.csv",sep = ";")
    
    actFeatures$Date<- as.Date(actFeatures$Date, "%d/%m/%Y")
    #Loading data
    rendimiento<-read.csv("Notas - 100-rendimiento_1.csv",sep = ";")
    
    #Getting means of activities
    activitiesMean<-data.frame(colnames(rendimiento[3:13]), colMeans(rendimiento[3:13]))
    names(activitiesMean)<-c("Activity", "Mean")
    activitiesMean<-merge(activitiesMean,actFeatures)
    activitiesMean<-activitiesMean[complete.cases(activitiesMean),]
    
    #Getting students performance by career
    perfbyCar<-aggregate(rendimiento$Rendimiento~rendimiento$CARRERA,FUN = mean)
    names(perfbyCar)<-c("career","performance")
    perfbyCar$performance<-perfbyCar$performance*100
    x<-perfbyCar$performance
    names(x)<-perfbyCar$career


```


## Data Description. Part 1

- The data were taken from the programming course 1, which is being conducted in the first year of the careers of engineering faculty.  

- The dataset describes the grades until April 2016 in the activities evaluated.

- So far have been assessed **`r sum(actFeatures[c(1:9,11,14),]$Value)`** points

- Performance of each student is calculated by adding the cumulative score of each activity with respect to the points assessed to date and is expressed as a percentage.

- The average performance of the group is **`r round(mean(rendimiento$Rendimiento)*100,2)`%**


--- .class #ddesc1 

## Data Description. Part 2

- The group is composed of **`r nrow(rendimiento)`** students from **`r length(unique(rendimiento$CARRERA))`** university careers:  

**_Students Distribution by Career_**
```{r echo=FALSE, results='markup'}
    Ctable<-table(rendimiento$CARRERA)
    Ctable
```



--- .class #ddesc2

## Exploratory Analysis. Part 1

- Students in this group have performance problems, as shown in the following chart:  
```{r echo=FALSE,fig.align='center', fig.height=6, fig.width=8}
    
    g <- ggplot(activitiesMean,aes(Date,Mean))+ geom_line( colour="#000099") + scale_x_date()
                    g <- g + xlab("Activities Date")
                    g <- g + ylab("Activities Mean")
                    g <- g + ggtitle("Average scores for the activities by date")
    model<-lm(Mean~Date,activitiesMean)
    g <- g + geom_abline(slope = model$coefficients[2], intercept = model$coefficients[1], colour="red")    
    g
```
- The tendency is to lower ratings.   
           

--- .class #expAn1 

## Exploratory Analysis. Part 2

```{r echo=FALSE}
    best <- nrow(rendimiento[rendimiento$Rendimiento>0.70,])
    percentage <- round((best/nrow(rendimiento))*100,1)
```

- As shown in the chart below, only **`r percentage`%** of the group has performance above 70%.  

```{r echo=FALSE, fig.align='center', fig.height=3, fig.width=5}
    g <- ggplot(data=rendimiento, aes(rendimiento$Rendimiento)) 
            g <- g + geom_histogram(breaks=seq(0, 1, by =.2), col="red",aes(fill=..count..))
            g <- g + scale_fill_gradient("Count", low = "yellow", high = "orange")
            g <- g + ggtitle("Histogram of students performance") 
            g <- g + xlab("Performance")
            g <- g + ylab("Frequecy")
    g

```
- Students of electronics and bioinformatics have better performance.
```{r echo=FALSE, fig.align='center', fig.height=3, fig.width=8}
 g <- ggplot(perfbyCar, aes(x=as.factor(career),y=performance, fill=career))
            g <- g + geom_bar(stat = "identity")
            g <- g + theme(axis.text.x=element_text(angle=25, hjust = 1))
            g <- g + ggtitle("Students performance by Career") 
            g <- g + xlab("Career")
            g <- g + ylab("Performance")
            g
```



